Developing a preprint culture in biology

### 2012-09-28 ms.tex
Minor changes; added to a few sentences about git

Submission to arXiv is fully automated.  Authors can submit \TeX/\LaTeX
documents that are compiled on the server or directly submit in PDF/PS format
(for example, as exported by a word processor).  A moderation system was put in
place in 2004: papers must be categorized by an endorser. At least one
author of a paper must be an endorser that has previously submitted a paper or
has received permission to submit to a particular category.  Many authors in
mathematics and physics submit papers as soon as they are ready for review by
colleagues, although another popular option is submitting simultaneously to a
journal and arXiv.

@@

This manuscript was developed entirely as an open project on github. github is a
hosting service for projects under the git revision control tool. git is a
decentralized revision control system used primarily to develop software. It
allows the users to share code, track changes, and merge versions. For example,
during the development of this manuscript, one author would fork the project
(that is: make a personal copy), modify it, and then the changes were merged
back into the main branch. These techniques are widely used in open source
software development. It goes even farther than submitting preprints by opening
the entire writing process.

@@

>>>>

Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
documents that are compiled on the server or directly submit in PDF/PS format
(for example, as exported by a word processor).  A moderation system was put in
place in 2004: papers must be categorized by an endorser. At least one
author of a paper must be an endorser that has previously submitted a paper or
has received permission to submit to a particular category.  Many authors in
mathematics and physics submit papers as soon as they are ready for review by
colleagues, although another popular option is submitting simultaneously to a
journal and arXiv.

@@

This manuscript was developed entirely as an open project on
github. github is one of several hosting services for collaborative
development using the git revision control software.  git is a
decentralized revision control system created by Linus Torvalds used
primarily to develop software, including the Linux kernel. It allows
the users to share code, track changes, and merge versions. For
example, during the development of this manuscript, one author would
fork the project (that is: make a personal copy), modify it, and then
the changes were merged back into the main branch. These techniques
are widely used in open source software development. It goes even
farther than submitting preprints by opening the entire writing
process.

@@

JJA is supported by NSF DEB-0614166 and NSF DEB-0919018.
